\documentclass{article}
\title{UPE 2015 Elections\author{Micah A. Thornton}}
\begin{document}
\maketitle{}
Hello everyone my name is Jennifer Dworak and I am the chapter advisor for SMU's Kappa Chapter. congratulations again for becoming the newest members in the most prestigious honor society devoted to the computer and information sciences. We really hope that you will continue the tradition of this chapter and become active members, we will be holding our chapter elections for the 2015/16 academic year next week. Please watch your inbox for more detailed instructions on how to vote as it will be done online using the orgs@smu interface. We have five chapter offices: President, Vice President, Treasurer, Corresponding and Recording Secretaries. The time commitment for each of these positions is really minimal, the president oversees monthly meetings, the vice presidents assists the president in planning events and assumes the presidents role if they are unable to attend a meeting. The treasurer helps deal with the student comptroller, and gives financial reports at each meeting (just telling how much money we have and what we spent on etc..) the recording secretary records the minutes of each meeting and reads them back at the following meetings. The corresponding secretary in conjunction with the president and vp are in charge of all chapter correspondance as well as keeping the orgs at smu page up to date. We really hope to have interest in these offices, if you are interested in holding an office at all, again minimal time commitment, then please indicate to one of the active members here tonight your interest, and follow up by sending a short paragraph detailing your experience and vision for the chapter to the current secretary Micah Thornton, you should all have his email address as you have been corresponding with him to RSVP etc. We hope to see you all active in the organization, and congratulations again. 
\end{document}