\documentstyle{article}
\title{UPE Opening\author{Micah A. Thornton}}
\begin{document}
\maketitle{}
    Hello everyone, my name is Micah Thornton, I am the current secretary for Upsilon Pi Epsilon, Congratulations to everyone in this room, it is no small honor that you were qualified for membership in this illustrious society. There is really just one final test before you are allowed to join this society, you must tell me what the decimal value the eleven candles before you represent. Just kidding, as you can see, there are actually eleven candles those that are lit represent ones and those that are unlit are zeroes. They therefore represent the binary string 11110101111, which is an interesting string as it displays symmetry, but that is beside the point, if you were to convert the string you would find that it represented the decimal value 1967, which is infact the year that Upsilon Pi Epsilon was founded. We are almost exactly 50 years old, and are still going very strong. We hope to extend many more honors to you as members of UPE, such as scholarships, as well as active member awards, such as graduation chords etc... There are always things that need to be done so if you would like to become active in the society there is certainly something available to you. Dr. Dworak, our chapter advisor, will talk briefly about our upcomming elections after the ceremony, if you would like to become a leader in the society, and run for office we would be very happy to have you on the team! The ceremonies through which you are about to pass are symbolic and are very interesting, they inculcate the virtues that are instilled in this society, we are very excited to have you joining us, and hope that you will get much use out of the chapters activities. As a short taster for next year, we are planning to have monthly meetings with small snacks or meals, at least two service events (with habitat for humanity), and at least two social events per semester. We are also planning two more initiations next year, one in the spring and one in the fall. As such we need you all to take a vested interest in the well being of the chapter, it really is made up by strong caring and willing individuals such as you, please be sure to run for an office next for next year, and to attempt to regularly attend meetings, you will really get out of this organization what you put into it. Again congratulations, and we hope to see you again next year! Now here is our current president Nicole Sliwa to read the invocation before we begin the ceremonies. 
\end{document}