
\documentclass{letter}
\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
\pagenumbering{gobble}
\begin{document}
Taken From: \textit{http://upe.acm.org/reg_new_members.html}

Chapter advisers and/or officers are responsible for forwarding the names and dues of new UPE initiates to the headquarters of UPE.
\textbf{The fee per member is a \$60 one-time fee.}

Member names submitted by each chapter are the same names that are used to produce the member certificate. There is normally a ten-day turnaround time for ordering these certificates. Rush orders (for immediate turnaround) will require the additional payment of \$15 for the FedEx fee.

Chapters are encouraged to send their new member list via email to upe@acm.org. (It is no longer necessary to include postal addresses for each member. Additional personal information will be supplied by each member when completing the registration process for the free ACM student membership.)

When submitting the list of new members, chapters are encouraged to include the permanent email addresses of each candidate [Campus-issued email addresses generally become inactive after graduation.] These addresses will be added to the UPE email address file. UPE will only use these addresses to distribute the regular ``UPE Newsbrief'' that is sent out via email to members and friends of UPE.

The new member list must include the chapter name, date of initiation ceremony and the postal address of the chapter. The fee per member is a \$60 one-time fee plus any additional order for UPE memorabilia. (The \$60 membership fee includes the UPE membership certificate and a Key Pin. In addition, student members will receive a one-year complimentary student membership in the ACM.) The amount due to UPE must be paid by check and made payable to UPSILON PI EPSILON (or via Paypal to upe@acm.org). UPE membership is for a lifetime.

All postal communications to UPE should be sent to:

Upsilon Pi Epsilon
California State University, Chico
c/o Dr. Orlando S. Madrigal
158 Wetlands Edge Road
American Canyon, CA 94503

Ph: (530) 518-8488
Fax: (707) 647-3560

upe@acm.org
\end{document}