\documentclass{article}
\usepackage{hyperref}
\title{\author{Micah A Thornton\\ Vice President}Upsilon Pi Epsilon Charter Review}
\begin{document}
\maketitle{}
\section{Organization History}

The computing and information disciplines are relatively young. Yet despite their comparative youth, the computing and information disciplines have had an unparalleled effect on almost every aspect of contemporary life. Indeed it is difficult to predict the ultimate place of the computer in our world.  It is the express purpose of Upsilon Pi Epsilon to promote the computing and information disciplines and to encourage their contribution to the enhancement of knowledge.

Upsilon Pi Epsilon (UPE) was first organized at Texas A\&M University, College Station, Texas, in 1967. The international organization now consists of chapters in various colleges and universities in North America and overseas.

\section{Mission Statement}

The mission of Upsilon Pi Epsilon is to recognize academic excellence at both the undergraduate and graduate levels in the Computing and Information Disciplines.

The Association will accomplish this mission through programs that:

    Enable outstanding students to obtain recognition of superior educational achievement that emphasizes the Computing and Information Disciplines as well as liberal arts, sciences, and other professional and interdisciplinary education in the context of individual and societal responsibilities,
    Assist in maximizing the personal and professional growth of students in UPE by financially supporting scholarships and other creative endeavors that include the discovery, integration, and application of knowledge,
    Establish significant partnerships with external constituencies interested in promoting and subsidizing high quality computing science education,
    Seek opportunities to extend individual memberships and chapter activities into additional environments yet to become identified.

\section{Guidelines and Goals}

Upsilon Pi Epsilon is an honorary society whose membership consists of outstanding undergraduate and graduate students in Computing and Information Disciplines. Only schools that offer a degree in a computing science-related discipline may be chartered. Likewise, prospective student members must be working toward a degree in Computing and Information Disciplines at the time they are considered for membership. Yet members are chosen not only for their scholastic achievement in a computing science program, but also for distinguishing themselves as true professionals by meeting the standards of the society. Membership is limited to those who can effectively achieve the original goals of the society. These goals include:

    The recognition of outstanding talent in the field of computing science,
    The promotion of high scholarship in computing science,
    The establishment and maintenance of high standards in computing science,
    The representation of computing science in interdisciplinary communications, and
    The encouragement of individual contributions to society through computing science.

\section{Endorsements and Affiliation}

Upsilon Pi Epsilon is the first and only, existing international honor society in the Computing and Information Disciplines. It has received endorsements from the two largest computer organizations in the world, the Association for Computing Machinery (ACM) and the IEEE Computer Society (IEEE-CS).

UPE is a member of the Association of College Honor Societies (ACHS).

\section{Summary}

    Upsilon Pi Epsilon:
    \begin{itemize}
    \item recognizes academic excellence in the Computing and Information Disciplines.
    \item has chapters in various colleges and universities in North America and overseas.
    \item is the only honor society that is recognized by the ACM and the IEEE-CS.
    \item presents scholarship awards to active members.
    \item present scholarship awards to student members of the ACM and the IEEE-CS.
    \item presents cash awards to chapters who send representatives to its annual convention.
    \item presents cash awards and plaques to all participating teams at the ACM International Scholastic Programming Contest.
    \item presents scholarship awards on behalf of industry supporters of the association.
    \item presents the ABACUS Award - our most prestigious award presented to an individual who, over several years, \item has provided extensive support and leadership for student-related activities in the Computing and Information Disciplines.
    \end{itemize}

\section{Chapter History}

    Kappa Chapter of Upsilon Pi Epsilon was founded in 2005 at SMU. There were 7 founding members. The chapter was initially advised by Mitchell Thornton, and Maggie Dunham.
 
\section{Chapter Reorganization}

    We have recently undergone a slight restructuring, and have moved to begin monthly meetings on the second tuesday of every month at 6:00 PM. We have additionally overhauled our invitation mechanisms to provide more specialized and individualized invitations to prospective members. We have a total of seventeen persons who will be initiated next week. We plan to hold officer elections shortly after the initation, roughly one week. This will be facilitated through the orgs@smu elections option. Please see below for a rough outline of proposed activities for the society before the end of the year. We will finish the orgs@smu consulati on as soon as possible, we would like to get in contact with those in charge of this program as soon as possible and would greatly appreciate their contact information. 

\section{Orgs-At-SMU consulation}

    Unfortunately we were not aware of the original timeline for this, and were subsequently unable to hold to it. We have restructured our orgs-at-SMU page, \hyperref[https://smu.collegiatelink.net/organization/upsilonpiepsilon/]{https://smu.collegiatelink.net/organization/upsilonpiepsilon/} and would like to attend and complete this consulation as soon as possible. Please inform us how we can efficiently complete this consulation.

\section{Organization Leadership}

    Our organization has five elected offices, they are: 
        \begin{enumerate}
        \item President - Oversees monthly meetings, and helps plan important events. 
        \item Vice President - Assists the president with his duties. 
        \item Treasurer - Oversees the operating accounts for our chapter, and prepares financial reports.
        \item Corresponding Secretary - Corresponds with Chapter membership.
        \item Recording Secretary - Records and reports chapter meeting minutes.
        \end{enumerate}
    We select our officers by through a regular election in which all members may run for, and vote for officers using the orgs@smu framework. We are planning to hold our next Elections on April 23, 2015. The current officers are shown below in the membership rooster. Note, the two secretary positions are sometimes combined based on chapter interest.

\section{Ongoing Benefit to the University Community}

    Upsilon Pi Epsilon's primary concern is the recognition of outstanding scholarship in the computer science and engeneering fields. However we are not solely an academic society, we are also a social and service society that takes pride in its contributions to community service projects and its presence in the community. For the duration of the year we are planning on a few events. Following the reception and initiation next week we plan to hold elections. Aside from our standard monthly meetings we are also in the process of planning a joint end of year barbeque with Tau Beta Pi, IEEE student society, and Eta Kappa Nu. We are also planning to perform a service project through the United Methodist Church's branch of Habitat for Humanity next month. UPE continues to serve its original purpose, and with this reinvigoration in membership and leadership we plan to become even more active. We are very excited about what the next year holds, but are going to continue our relationship with Habitat for Humanity, and continue hosting social events, such as awards banquets, initations, dinners, bowling, etc... 

\section{Adherence to Founding Documents}

    Please find both the national and chapter bylaws attached to this document, we take pride in our strict adherence to the founding members and advisors vision for the society. 

\section{Membership Rooster}

    \begin{center}
    \begin{tabular}{| c | c | c | }
    \hline
    Last Name & First Name & Position\\\hline\hline
    Dworak & Jennifer & Chapter Advisor \\ \hline
    Sliwa & Nicole & President \\\hline
    Thornton & Micah & Vice President \\\hline
    Solis & Candie & Treasurer \\ \hline
    Kohli & Vipul & Secretary \\ \hline
    Scruggs & John & \\\hline
    Smith & Lauryn & \\\hline
    Lomeo & James & \\\hline
    Friman & Raz & \\
    \hline
    Cheng & Alexander & \\
    \hline



    \end{tabular}
    \end{center}
\section{Tentative Schedule for Rest Of Academic Year}

    \centering
    \begin{tabular}{| c | c |}
    \hline 
    event & date \\ 
    \hline\hline
    Spring 2015 Initation & April 21 \\ 
    2015 Elections & April 23 \\ 
    Habitat Service day & April 25 \\ 
    Monthly Meeting & May 12 \\ 
    End of Year BBQ & May 14 \\
    \hline
    \end{tabular}
\end{document}